Laziness in R

### 2019-02-09 report/report.Rmd
Fix evaluation depth reduction, summarization, visualization, report

>>>>

## Argument execution time

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_execution_time_by_parameter_class.png")
```

## Promise Evaluation

### Call Depth

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_count_by_call_depth_and_expression_type.png")
```

```{r echo = FALSE}
show_table("argument_count_by_call_depth_and_expression_type")
```

### Promise Depth

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_count_by_promise_depth_and_expression_type.png")
```

```{r echo = FALSE}
show_table("argument_count_by_promise_depth_and_expression_type")
```

### Nested Promise Depth

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_count_by_nested_promise_depth_and_expression_type.png")
```

```{r echo = FALSE}
show_table("argument_count_by_nested_promise_depth_and_expression_type")
```
